---
title: "Future projections from AWI-CMIP6 model (6 variables, best algo from ffs)"
author: "Philippine Chambault"
date: "03/07/2022"
output: 
  bookdown::html_document2:
    number_sections: yes
    code_folding: show
    df_print: default
    fig_caption: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo      = TRUE,
  fig.align = "center",
  message = FALSE,
  warning = FALSE,
  cache   = FALSE,
  out.width = "100%",
  comment = NA
)
```
```{r global_options, include=FALSE}
library(viridis)
library(raster)
library(maps)
library(gridExtra)
library(tidyquant)
library(tidyverse)
library(dplyr)
library(RColorBrewer)
library(ggmap)
library(dplyr)
library(ncdf4)
library(fields)
library(rgeos)
```


# Context 

One GCM at a 25 km resolution were tested ("AWI-CM-1-1-MR"), including _Sea Surface Temperature_ (tos), _Sea Surface Salinity_ (sos), _Sea Surface Height_ (zos) and _Mixed Layer Depth_ (mlotst). These 4 dynamic variables were first (i) extracted from CMIP6 for the historical period (1993-2014) and contemporary period (2015-2020) from ssp126. Then, each variable was included in the initial models run on the available dataset (current predictions: "present").

The results here are presented for summer only.










# Belugas {.tabset}

```{r, echo=F}
north_map = map_data("world") %>% group_by(group)
shore     = north_map[north_map$region=="Canada" 
                      | north_map$region=="Greenland"
                      | north_map$region=="Norway"
                      | north_map$region=="Russia"
                      | north_map$region=="Sweden"
                      | north_map$region=="Denmark"
                      | north_map$region=="Finland"
                      | north_map$region=="Iceland",]

```

## Present NNET
```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/5.CARET/Bel_West/Predictions/Summer/AWI-CM-1-1-MR/Average_6var_bestAlgo/PredMean_ffs_bestAlgo_Summer_6var_AWI-CM-1-1-MR_Bel_West.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Max prediction maps for belugas in present summer from the NNEt."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") + 
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Summer present, NNET") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


## Mean 2030 NNET
```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2030.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2030 from the NNET (ssp126)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_point(data=m, aes(x,y,z=layer, colour=layer), size=1, stroke=0) +
  # scale_colour_distiller(palette="BuPu", direction=1,limits=c(0,1)) +
  # geom_tile(data=m, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1,
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2030 (NNET, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2030.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2030 from the NNET (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_tile(data=m, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1,
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2030 (NNET, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


## Mean 2060 NNET
```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2060.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2060 from the NNET (ssp126)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=m, aes(x,  y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1, 
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2060 (NNET, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2060.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2060 from the NNET (ssp585)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=m, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1, 
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2060 (NNET, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```



## Mean 2100 NNET
```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2100.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2100 from the NNET (ssp126)."}
ggplot(shore, aes(long, lat)) +
  # geom_tile(data=m, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1,
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2100 (NNET, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
m <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bel_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bel_West_2100.rds")
m <- as_tibble(rasterToPoints(m))
```

```{r, echo=FALSE, NNET="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Belugas in summer 2100 from the NNET (ssp585)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=m, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=m, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1, 
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,-40), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Belugas",
       subtitle="Mean Summer 2100 (NNET, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```















# Narwhals {.tabset}

## Present (BRT)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/5.CARET/Nar_West/Predictions/Summer/AWI-CM-1-1-MR/Average_6var_bestAlgo/PredMean_ffs_bestAlgo_Summer_6var_AWI-CM-1-1-MR_Nar_West.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/5.CARET/Nar_East/Predictions/Summer/AWI-CM-1-1-MR/Average_6var_bestAlgo/PredMean_ffs_bestAlgo_Summer_6var_AWI-CM-1-1-MR_Nar_East.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean prediction maps for Narwhals in present summer from the BRT."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=west, aes(x,y, fill=layer)) +
  # geom_tile(data=east, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1, 
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Summer present, BRT") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```



## Mean 2030 (BRT)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2030.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_East_2030.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2030 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # scale_fill_brewer(palette="BuPu") +
  geom_tile(data=west, aes(x,y, fill=layer)) +
  geom_tile(data=east, aes(x,y, fill=layer)) +
  scale_fill_distiller(palette="BuPu", direction=1,
                       limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2030 (BRT, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2030.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_East_2030.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2030 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # scale_fill_brewer(palette="BuPu") + 
  geom_tile(data=west, aes(x,y, fill=layer)) +
  geom_tile(data=east, aes(x,y, fill=layer)) +
  scale_fill_distiller(palette="BuPu", direction=1, 
                       limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2030 (BRT, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```






## Mean 2060 (BRT)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2060.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_East_2060.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2060 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # scale_fill_brewer(palette="BuPu") +
  geom_tile(data=west, aes(x,y, fill=layer)) +
  geom_tile(data=east, aes(x,y, fill=layer)) +
  scale_fill_distiller(palette="BuPu", direction=1,
                       limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2060 (BRT, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2060.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_East_2060.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2060 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # scale_fill_brewer(palette="BuPu") + 
  geom_tile(data=west, aes(x,y, fill=layer)) +
  geom_tile(data=east, aes(x,y, fill=layer)) +
  scale_fill_distiller(palette="BuPu", direction=1, 
                       limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2060 (BRT, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```





## Mean 2100 (BRT)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2100.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_East_2100.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2100 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=west, aes(x,y, fill=layer)) +
  # geom_tile(data=east, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1, 
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2100 (BRT, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_West_2100.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Nar_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Nar_east_2100.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Narwhals in summer 2100 from the BRT (ssp585)."}
ggplot(shore, aes(long, lat)) +
  # geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  # scale_fill_brewer(palette="BuPu") + 
  geom_tile(data=west, aes(x,y, fill=layer)) +
  geom_tile(data=east, aes(x,y, fill=layer)) +
  scale_fill_distiller(palette="BuPu", direction=1, 
                       limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,0), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Narwhals",
       subtitle="Mean Summer 2100 (BRT, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```












# Bowheads {.tabset}

## Present (NNET)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/5.CARET/Bw_West/Predictions/Summer/AWI-CM-1-1-MR/Average_6var_bestAlgo/PredMean_ffs_bestAlgo_Summer_6var_AWI-CM-1-1-MR_Bw_West.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/5.CARET/Bw_East/Predictions/Summer/AWI-CM-1-1-MR/Average_6var_bestAlgo/PredMean_ffs_bestAlgo_Summer_6var_AWI-CM-1-1-MR_Bw_East.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean prediction maps for Bowheads in present summer from the NNET."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") +
  # geom_tile(data=west, aes(x,y, fill=layer)) +
  # geom_tile(data=east, aes(x,y, fill=layer)) +
  # scale_fill_distiller(palette="BuPu", direction=1,
  #                      limits=c(0,1), breaks=seq(0,1,by=0.2)) +
  coord_map("azequidistant", xlim=c(-105,80), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Bowheads",
       subtitle="Summer present, NNET") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```






## Mean 2030 (NNET)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_West_2030.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_East_2030.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Bowheads in summer 2030 from the NNET (ssp126)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") + 
  coord_map("azequidistant", xlim=c(-105,80), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Bowheads",
       subtitle="Mean Summer 2030 (NNET, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```



```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_West_2030.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_East_2030.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Bowheads in summer 2030 from the NNET (ssp585)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") + 
  coord_map("azequidistant", xlim=c(-105,80), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Bowheads",
       subtitle="Mean Summer 2030 (NNET, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```






## Mean 2100 (NNEt)
```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_West_2100.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp126/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_East_2100.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Bowheads in summer 2100 from the NNET (ssp126)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") + 
  coord_map("azequidistant", xlim=c(-105,80), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Bowheads",
       subtitle="Mean Summer 2100 (NNET, ssp126)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```


```{r, echo=F}
west <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_West/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_West_2100.rds")
west <- as_tibble(rasterToPoints(west))

east <- readRDS("/Users/philippinechambault/Documents/POST-DOC/2021/PAPER3/RDATA/6.Climatic_projections/Bw_East/0.25deg/Summer/AWI-CM-1-1-MR_ssp585/Average_6var/ProjMean_Summer_0.25deg_6var_10runs_bestAlgo_Bw_East_2100.rds")
east <- as_tibble(rasterToPoints(east))
```

```{r, echo=FALSE, fig.pos="placeHere", fig.height=4,fig.cap="\\label{fig:figs}Mean projection maps for Bowheads in summer 2100 from the NNET (ssp585)."}
ggplot(shore, aes(long, lat)) +
  geom_contour_filled(data=west, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  geom_contour_filled(data=east, aes(x,y,z=layer), breaks=seq(0,1,by=0.2)) +
  scale_fill_brewer(palette="BuPu") + 
  coord_map("azequidistant", xlim=c(-105,80), ylim=c(60,80)) +
  scale_y_continuous(breaks=c(60,70), labels=c(60,70)) +
  geom_polygon(aes(group=group), fill="lightgrey",lwd=1) +
  labs(y="",x="",fill="Habitat \nsuitability",title="Bowheads",
       subtitle="Mean Summer 2100 (NNET, ssp585)") + 
  theme(axis.text.y  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks   = element_blank(),
        strip.background = element_rect(fill="gray52", size=0.1),
        strip.text = element_text(colour='black',size=12,face="bold",
                                  margin=margin(0.1,0.1,0.1,0.1,"cm")),
        axis.title = element_text(size=12,face="bold", hjust=0.5),
        panel.border = element_rect(colour="black",fill=NA,size=0.2),
        legend.key.size = unit(0.5,"line"),
        legend.key.width = unit(0.14,"cm"),
        legend.key.height = unit(0.3,"cm"),
        legend.title = element_text(size=7),
        legend.text = element_text(size=7),
        legend.box.spacing = unit(0.1,'cm'),
        legend.margin=margin(t=-0.0, unit='cm'),
        legend.key = element_blank(),
        panel.spacing.x = unit(0.07, "lines"),
        panel.spacing.y = unit(0.07, "lines"),
        title = element_text(colour="black",size=14,face="bold"),
        plot.title=element_text(size=14, vjust=-0.5, hjust=0),
        panel.background = element_blank(),
        panel.grid.major = element_line(colour="gray52", size=0.1),
        plot.margin = unit(c(0,0.1,-1,-0.4),"cm")) 
```
